\section{Repository Structure}
The implementation resides in a monorepo-style layout:
\begin{itemize}
  \item \texttt{client/} --- Vite React application (\texttt{src/pages}, \texttt{components}, \texttt{layouts}, \texttt{services}, \texttt{store}).
  \item \texttt{server/} --- Express application (\texttt{src/models}, \texttt{routes}, \texttt{controllers}, \texttt{services}, \texttt{middleware}, \texttt{seed}).
\end{itemize}

\section{Frontend}
\subsection{Navigation and Guards}
\texttt{ProtectedRoute} waits for session hydration then enforces authentication. \texttt{RoleRoute} restricts routes by role (admin, manager, employee). \texttt{DashboardLayout} provides sidebar navigation and profile menu with logout calling \texttt{/api/auth/logout}.

\subsection{Forms and Validation}
React Hook Form with Zod resolvers validates login, registration, employee, and task forms. User-facing errors render inline; global feedback uses toast notifications.

\subsection{Dashboards and Charts}
Recharts renders bar, line, area, and pie charts fed by existing APIs (employees, tasks, alerts, performance trends). This avoids duplicating aggregation logic in the client.

\section{Backend}
\subsection{Models}
Mongoose schemas enforce enums (e.g.\ task status, alert type), references (\texttt{assignedTo}, \texttt{employeeId}), and timestamps. Pre-validate hooks ensure OAuth users do not require local passwords.

\subsection{Performance Engine}
Given employee metrics and optional overrides, the engine reads weights from \texttt{AppSettings}, normalises weights to sum~1, clamps inputs to $[0,100]$, applies safe defaults for missing values (recorded in \texttt{defaultsUsed}), computes contributions, and builds a short narrative comparing factors above/below the employee's local mean.

\subsection{Task Allocation}
For each active employee, compute skill match ratio, availability from workload, penalty from workload and active assignment count, and $\text{final} = \text{match} + \text{availability} - \text{penalty}$. Sort and slice top three; flag manual review when confidence is low.

\subsection{Attrition, Anomaly, Promotion}
Attrition uses additive rule scores with capped total and categorical bands. Anomaly service scans recent \texttt{PerformanceRecord} series for z-score style drops and heuristic rules (attendance delta, completion volatility, empty history). Promotion ranks employees with weighted factors and explanatory strings.

\subsection{Seeding}
\texttt{npm run seed} clears demo collections and inserts administrators, managers, many employees, tasks in multiple states, six monthly performance snapshots per employee, and diverse alerts---supporting immediate UI demonstration.

\section{Configuration}
Environment variables (\texttt{.env}) control MongoDB URI, JWT secret and expiry, client URL for CORS, and optional Google OAuth credentials. Example files document required keys without committing secrets.

\section{Tooling}
Server development uses \texttt{nodemon}; client uses Vite HMR. Production build: \texttt{npm run build} for static assets served separately from API.
