\section{Demonstration Scenarios}
The seeded dataset includes multiple departments, twenty-two employee profiles, twenty-five tasks (pending, assigned, in-progress, completed), six historical performance records per employee, and fourteen alerts. Typical demo flows:

\begin{enumerate}
  \item \textbf{Authentication:} login as administrator; verify redirect to admin dashboard; logout and repeat as manager and employee-linked accounts.
  \item \textbf{Employee and task CRUD:} create or edit an employee; create a task; verify list filters and detail views.
  \item \textbf{Task allocation:} open allocation page, select an unassigned or low-confidence task, fetch top-three recommendations, inspect textual explanations, optionally auto-assign.
  \item \textbf{Performance:} run calculate for a selected employee; observe weighted score, contribution breakdown chart, and stored explanation; open trend list.
  \item \textbf{Anomaly scan:} from performance page, execute explainable scan; review anomaly types and suggested actions.
  \item \textbf{Attrition and promotion:} run attrition for a high-load employee; run promotion ranking with optional department filter.
  \item \textbf{Settings:} (admin) adjust weights, save, recalculate performance to show policy sensitivity.
\end{enumerate}

\section{Functional Verification}
Manual checklist aligned with project goals:
\begin{itemize}
  \item Registration and login succeed; protected routes reject unauthenticated access.
  \item Google login behaves as expected when OAuth env vars are configured; otherwise API returns a clear \texttt{503} message.
  \item Employee and task APIs respect role scoping (employee sees self).
  \item Recommendation API returns three or fewer candidates with fields \texttt{skillMatchScore}, \texttt{availabilityScore}, \texttt{workloadPenalty}, \texttt{finalMatchScore}, and \texttt{explanation}.
  \item Performance API persists breakdown and explanation; trends endpoint returns chronological points.
  \item ML endpoints always include explanatory prose and method/factor detail suitable for viva discussion.
\end{itemize}

\section{Observations}
Charts populate without manual data entry post-seed, improving repeatability for examination. Explainable strings make it straightforward to justify outputs during evaluation. Rule-based analytics trade some predictive power for transparency---an acceptable engineering choice for the stated academic scope, with a natural upgrade path to trained models using the same feature vectors.

\section{Limitations}
Results depend on seeded and manually entered metrics; no integration with live attendance hardware or payroll. OAuth and cookie behaviour should be revalidated against production hosting (HTTPS, SameSite policies). Load and security testing beyond basic hardening are not claimed.
