\section{Summary}
This project delivered \textbf{InsightHR}, an \textbf{Intelligent Employee Management \& Decision Support System}, combining conventional HR data management with transparent analytics: weighted performance scoring with configurable policy weights, skill- and workload-aware task recommendations, attrition and anomaly signals, and promotion-oriented ranking. The implementation spans a React client and an Express/MongoDB backend with JWT authentication and optional Google OAuth, organised into maintainable modules and validated APIs.

\section{Contributions}
\begin{itemize}
  \item Integration of \textbf{explainability} as a first-class output (not an afterthought) across scoring and ML-style endpoints.
  \item A \textbf{demo-ready} seed corpus enabling dashboards and charts without manual setup.
  \item Clear separation of \textbf{controllers} and \textbf{analytics services} to support future model swaps.
\end{itemize}

\section{Future Work}
\begin{itemize}
  \item Replace selected rule engines with trained models (e.g.\ logistic regression, gradient boosting) using exported feature rows; retain explanation via SHAP-like approximations or rule extraction for academic compliance.
  \item Add workflow approvals (task assignment, promotion) with audit trails.
  \item Integrate calendar or attendance feeds for automated metric refresh.
  \item Harden for production: rate limiting, refresh tokens, structured logging, automated tests (Jest/Cypress).
\end{itemize}

\section{Closing Remarks}
The system demonstrates that a capstone project can go beyond CRUD by embedding decision-support logic that remains understandable to non-experts---a practical balance between sophistication and integrity suitable for organisational pilots and academic assessment.
